Embodied Neuromorphic Benchmarks

### 2015-08-06 paper/paper.tex
intro

    Evaluating the effectiveness and performance of neuromorphic hardware is
    difficult.  It is even more difficult when the task of interest is an
    embodied task; that is a task where the output from the neuromorphic
    hardware affects its future input.  However, these embodied situations
    are one of the primary potential uses of neuromorphic hardware.  To address
    this, we present a methodology for embodied benchmarking and a particular
    example of a benchmark for adaptive control of an arbitrary system.  These
    benchmarks are flexible, in that they allow researchers to explicitly
    modify the benchmark to identify particular task domains where particular
    hardware excels.  Furthermore, the benchmarks make use of a hybrid of
    real physical embodiment and a type of "minimal" simulation that has been
    shown to lead to robust real-world performance, allowing the same benchmark
    to be used by many researchers.

@@

>>>>

    Evaluating the effectiveness and performance of neuromorphic hardware is
    difficult.  It is even more difficult when the task of interest is an
    embodied task; that is, a task where the output from the neuromorphic
    hardware affects its future input.  However, these embodied situations
    are one of the primary potential uses of neuromorphic hardware.  To address
    this, we present a methodology for embodied benchmarking and a particular
    example of a benchmark for adaptive control of an arbitrary system.  These
    benchmarks are flexible, in that they allow researchers to explicitly
    modify the benchmark to identify particular task domains where particular
    hardware excels.  Furthermore, the benchmarks make use of a hybrid of
    real physical embodiment and a type of "minimal" simulation that has been
    shown to lead to robust real-world performance, allowing the same benchmark
    to be used by many researchers.

@@

Neuromorphic hardware holds great promise for a wide variety of applications.
The combination of massively parallel computation and low power consumption
means that there is the potential to have complex algorithms running in
embedded processing situations, without being a significant drain on battery
life.  The question, of course, is to identify what sort of always-on or
interactive functionality is feasible with these devices.

To evaluate applications of this hardware, we need benchmark tasks.  These
tasks must allow us to compare across different instances of neuromorphic
hardware (and potentially across different algorithms implemented in said
hardware).  This allows us to quantitatively compare systems, letting 
researchers both measure the progress in the field and also directly
compare competing approaches.

In this paper, we focus on the development of \emph{embodied} benchmarks.
These are tasks where the output of the neuromorphic hardware \emph{influences
its own future input}.  This is in contrast to standard categorization or pattern
identification tasks, where the input is some fixed sequence, and the main
question is whether the hardware produces the correct output for each input
(or input pattern).

We believe embodied benchmarks
